---
title             : "Mental simulation of routes during navigation involves adaptive
temporal compression"
shorttitle        : "MIDTERM: Routes of Mental simulation"

author: 
  - name          : "Aiden E.G.F. Arnold"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Giuseppe Iaria"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Calgary"
  - id            : "2"
    institution   : "University of California"

authornote: |
  Department of Psychology, Hotchkiss Brain Institute and Alberta Children’s Hospital Research Institute, University of Calgary, Calgary, Alberta, Canada
  Center for Neuroscience, University of California, Davis, 1544 Newton Court, Davis, CA, USA


abstract: |
 [@Arnold_2016] is an experiment to exmaine the temporal and spatial aspects of memory through the use of virtual simulations. Specifically, in the following experiment,, to examined whether their is a relationship between mental simulations and the ability to navigate the fastest route.
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "500"

bibliography      : ["r-references.bib", "biblio.references"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods

## Participants

Twenty-eight participants were used with two participants being excluded for responding with mean reaction
times of less than 1 second and failure to complete the simulation phase due to sickness.

## Material

## Procedure
Participants were navigated through a virtual city. First they were shown landmarks, ask to locate them, and then find the shortest path to the landmarks.

## Data analysis
We used `r cite_r("r-references.bib","bibio.references")` for all our analyses.




# Results

```{r, eval=F}
Ori_dataset <- read_csv("Ori_dataset.csv")

Ori_dataset[is.na(Ori_dataset)]<-0



library(dplyr)
library(data.table)
library(ggplot2)

```



```{r,eval=F}

Ori_dataset[is.na(Ori_dataset)]<-0
Ori_dataset

data3 <- Ori_dataset %>% filter(RT>1) 


ALL <- plot(data3$Path_Time, data3$Sim_Centered, main="ALL", xlab="Excess Path Time ", ylab="Mean Centered Simulation Time")

abline(lm(data3$Sim_Centered~data3$Path_Time), ALL, col="purple")


cor.test(data3$Sim_Centered, data3$Path_Time)

# There is a positive correlation in the all the simulations together with a r(532)=0.2853851, p=1.822e-11.

```


```{r,eval=F}

Ori_dataset[is.na(Ori_dataset)]<-0
Ori_dataset

S <- Ori_dataset %>% filter(Group==2)

SLOW <- plot(S$Path_Time, S$Sim_Centered, main="SLOW", xlab="Excess Path Time ", ylab="Mean Centered Simulation Time")

abline(lm(S$Sim_Centered~S$Path_Time), SLOW, col="purple")

cor.test(S$Sim_Centered, S$Path_Time)

# There is a positive correlation in the slow simulations with a r(258)=0.122393, p=0.04867.

```

```{r,eval=F}

Ori_dataset[is.na(Ori_dataset)]<-0
Ori_dataset

M <- Ori_dataset %>% filter(Group==1)

MEDIUM <- plot(M$Path_Time, M$Sim_Centered, main="MEDIUM", xlab="Excess Path Time ", ylab="Mean Centered Simulation Time")

abline(lm(M$Sim_Centered ~ M$Path_Time), MEDIUM, col="purple")

cor.test(M$Sim_Centered, M$Path_Time)

# There is a positive correlation in the medium condition simulations with a r(278)=0.1381928, p=0.02071

```

```{r,eval=F}

Ori_dataset[is.na(Ori_dataset)]<-0
Ori_dataset

Ft <- Ori_dataset %>% filter(Group==1)

FAST <- plot(Ft$Path_Time, Ft$Sim_Centered, main="FAST", xlab="Excess Path Time ", ylab="Mean Centered Simulation Time")

abline(lm(Ft$Sim_Centered ~ Ft$Path_Time), FAST, col="purple")

cor.test(Ft$Sim_Centered, Ft$Path_Time)

# There is a positive correlation in the fast condition simulations with a r(278)=0.1381928, p=0.02071

```
# Power Analysis
```{r, eval=F}
library(pwr)

length(Ft)
pwr.r.test(n=20, r= NULL , sig.level = 0.05, power=.8)


es <- seq(.1,2,.1)
power <- sapply(es, 
          FUN = function(x) {
            pwr.r.test(n=20, r= x , sig.level = 0.05)$power})
Power_Curve <- data.frame(es,power)

library(ggplot2)
ggplot(Power_Curve, aes(x=es,
                    y=power))+
  geom_point()+
  geom_line()

# es = effect size
```

# Discussion
The analysis failed to replicate the results of [@Arnold_2016]. This is believed to be a result of trouble identifying the conditions (groups slow, medium, and fast movement groups) from the dataset.


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
